Hydras \& Co.

### 2022-04-06 doc/gaia-chapter.tex
corrections chapter 7 (completed)
make E0 an eqtype
simplification of notations

The modules are named {\texttt{theories/gaia/*.v}} and coqdocumented in {\texttt{theories/html/gaia\_hydras.*.html}}
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.
Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

@@

\inputsnippets{T1Bridge/limitbRef, T1Bridge/isSuccRef}

@@

\subsection{A type for well-formed ordinal terms}

For compatibility's sake, we add a clone of \texttt{hydra-battles}' type \texttt{E0} defined in \href{../theories/html/hydras.Epsilon0.E0.html}{Epsilon0.E0}.

@@

\inputsnippets{T1Bridge/E0EqP}

@@

>>>>

The modules are named {\texttt{theories/gaia/*.v}} and coqdocumented in \linebreak {\texttt{theories/html/gaia\_hydras.*.html}}
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.
Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

@@

\inputsnippets{T1Bridge/limitbRef}
\inputsnippets{T1Bridge/isSuccRef}

@@

\subsection{A type for well-formed ordinal terms}
\label{sect:E0-gaia-hydras}
For compatibility's sake, we add a clone of \texttt{hydra-battles}' type \texttt{E0} defined in \href{../theories/html/hydras.Epsilon0.E0.html}{Epsilon0.E0}.

@@

@@

\section{Already ported definitions and lemmas}

\textbf{These tables are still in construction.}

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Types for ordinals less than $\epsilon_0$}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Hydras & page & Gaia-Hydras& page& Description \\\hline
  \texttt{T1.T1} 
       &  \pageref{types:T1}
              & \texttt{CantorOrdinal.T1}
                           &  & ordinal terms \tnote{1} \\

  \texttt{E0.E0}
       & \pageref{types:E0}
              & \texttt{T1Bridge.E0}
                           & \pageref{sect:E0-gaia-hydras}
                                 & ordinal terms in Cantor normal form \\

  \texttt{ON\_Finite.t}
       & \pageref{def:Finite-ord-type}
              & \ssreflect's finite ordinals \tnote{2}&  & ordinals below $\omega$ \\
\hline
\end{tabular}
\begin{tablenotes}
  \item[1] From \gaia library.
   \item[2] From \ssreflect/\mathcomp libraries.
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2022-04-06 doc/hydras.tex
corrections chapter 2
corrections chapter 5 (up to p. 106)
simplification of notations

\newcommand{\gaiacompat}{\textcolor{blue}{Gaia}}
\newcommand{\gaiasign}{\texorpdfstring{\mycircled[cyan!40]{{\mbox{\color{blue}{\scriptsize{G}}}}}}{Gaia-Hydra}}
\newtheorem{gaiahydra}{\gaiasign}

@@

Our library \gaiaHydras is dedicated to make compatible our lemmas with José Grimm's \gaia project (designed for \ssreflect/\mathcomp).

@@

\subsection{Alternative or bad definitions}
\label{sect:alt-proofs}
Finally, we decided to include definitions or lemma statements, as well as tactics,  that lead to
dead-ends or too complex developments, with the following coloring.
Bad definitions 
 are ''masked '' inside modules called \texttt{Bad}, \texttt{Bad1}, etc.

>>>>

\newcommand{\gaiacompat}{\textcolor{blue}{Gaia}}
\newcommand{\gaiasign}{\texorpdfstring{\mycircled[orange!40]{{\mbox{\color{blue!65}{\scriptsize{G}}}}}}{Gaia-Hydra}}
\newtheorem{gaiahydra}{\gaiasign}

@@

Our library \gaiaHydras is dedicated to make compatible our lemmas with José Grimm's \gaia project (designed for \ssreflect/\mathcomp) (please look at Sect.~\vref{sect:gaia-first-intro} and the paragraphs signalled with {\gaiasign}).

@@

\subsection{Alternative or bad definitions}
\label{sect:alt-proofs}
Finally, we decided to include definitions or lemma statements, as well as tactics,  that lead to
dead-ends or too complex developments, with the following coloring.
Bad definitions 
 are ''masked'' inside modules called \texttt{Bad}, \texttt{Bad1}, etc.

### 2022-04-06 doc/part-hydras.tex
simplification of notations

\subsection*{Compatibility with \gaia (in progress)}
The \gaia project~\cite{Gaia} by Jos\'e Grimm, Alban Quadrat,  and Carlos Simpson,
aims  to formalize mathematics in \coq  in
the style of Nicolas Bourbaki. It contains many definitions and results about ordinal numbers. In Chapter~\ref{gaia-chapter}, we present some modules which allow \HydrasLib' users to apply lemmas proven in \gaia, and vice versa. Remarks about compatibility with \gaia are signalled with the picture \gaiasign.

@@

\label{def: Finite-ord-type}

@@

@@

%ICI

@@

\subsection{Comparison between \texttt{L\_} and \texttt{H'\_} }

>>>>

 \subsection*{Compatibility with \gaia (in progress)}
 \label{sect:gaia-first-intro}
The \gaia project~\cite{Gaia} by Jos\'e Grimm, Alban Quadrat,  and Carlos Simpson,
aims  to formalize mathematics in \coq  in
the style of Nicolas Bourbaki. It contains many definitions and results about ordinal numbers. In Chapter~\ref{gaia-chapter}, we present some modules which allow \HydrasLib' users to apply lemmas proven in \gaia, and vice versa. Remarks about compatibility with \gaia are signalled with the picture \gaiasign.

@@

\label{def:Finite-ord-type}

@@

\paragraph*{\gaiasign}
The module
\href{../theories/html/gaia_hydras.GL_alpha.html}{gaia\_hydras.GL\_alpha} contains an adaptation of
\href{../theories/html/hydras.Epsilon0.L_alpha.html}{Epsilon0/L\_alpha}.

@@

\paragraph*{\gaiasign}
The module
\href{../theories/html/gaia_hydras.GHprime.html}{gaia\_hydras.GHprime} contains an adaptation of
\href{../theories/html/hydras.Epsilon0.Hprime.html}{Epsilon0.Hprime}.

@@

%ICI
\subsection{Comparison between \texttt{L\_} and \texttt{H'\_} }
